Supplementary figures for Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis

### 2020-12-01 manuscript/supplementary_figures.Rmd
supplementary tables added: treatment combinations and outcomes by hospital

>>>>

# Table \@ref(tab:treatment_comb_table} gives overview of combinations of treatments used in individual patients.
```{r treatment_comb_table, echo=FALSE}
pd<-data$patient_data
x<-sort(table(paste0(
 as.numeric(pd$ever_hcq),
 as.numeric(pd$ever_az),
 as.numeric(pd$ever_convalescent_plasma),
 as.numeric(pd$ever_favipiravir),
 as.numeric(pd$ever_remdesivir),
 as.numeric(pd$ever_dexamethasone),
 as.numeric(pd$ever_antibiotics))),dec=TRUE)
x2<-c()
nms<-c('HCQ','AZ','Plasma','Favipiravir','Remdesivir','Dexamethasone','ATB')
for (i in 1:length(x)) {
 x3<-c()
 for (i2 in 1:nchar(names(x)[i])) {
   x3<-c(x3,ifelse(substring(names(x)[i],i2,i2)=='1',nms[i2],''))
 }
 x2<-rbind(x2,cbind(n=x[i],rbind(x3)))
}
rownames(x2)<-c()
colnames(x2)<-c('N',nms)
x2<-x2[,c(1,2,3,8,4:7)]
knitr::kable(x2,caption = "Treatment combinations in individual patients.", booktabs = TRUE)
```

```{r outcome_by_hospital_prepare, echo=FALSE}
tmp<-data$patient_data[,c('patient_id','hospital_id','outcome')]
tmp$outcome[tmp$outcome=='Transferred']<-'Hospitalized'
tmp$outcome<-dropLevels(tmp$outcome)
tmp$hospital_id<-factor(tmp$hospital_id)
levels(tmp$hospital_id)<-paste('H',1:length(levels(tmp$hospital_id)),sep='')
```

There were large differences between hospitals in the ratio of fatal outcomes 
(P=`r round(fisher.test(with(tmp,table(outcome,hospital_id)),simulate.p.value=T)$p.value,5)`).
```{r outcome_by_hospital, echo=FALSE}
knitr::kable(with(tmp,table(outcome,hospital_id)),caption = "Overview of outcomes in different hospitals. Note that at H6, 9 out of 19 patients died, while at H9, no patient died out of 9 patients treated.", booktabs = TRUE)
```
